\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-07-18 paper.qmd
Added CFA citations
Update Figure4 with quollr 0.1.5

## hexagon binning to have regular hexagons
hb_obj_scurve <- hex_binning(
  data = umap_scurve_scaled, 
  bin1 = num_bins_x_scurve, 
  r2 = r2)

@@

a2 <- tibble(x = all_centroids_df$c_x[27],
             xend = all_centroids_df$c_x[27],
             y = all_centroids_df$c_y[27],

@@

XXX Model in \gD{}, on the UMAP layout, and three views of the fit in projections from $7\text{-}D$, for the S-curve data. The model closely fits the shape, but it has breaks which means that it does not adequately capture the surface. (The **langevitour** software is used to view the data with a tour, and the full video is available at (<https://youtu.be/N6iWEj3aVps>). 
:::

@@

The model here is similar to a confirmatory factor analysis model (REF), $\widehat{T}(X_1, X_2, X_3) + \Epsilon$. The difference between the fitted model and observed values would be considered to be residuals, and for this problem are $7\text{-}D$.

>>>>

## hexagon binning to have regular hexagons
hb_obj_scurve <- hex_binning(
  data = umap_scurve_scaled, 
  bin1 = num_bins_x_scurve, 
  r2 = r2,
  q = 0.1)

@@

a2 <- tibble(x = all_centroids_df$c_x[25],
             xend = all_centroids_df$c_x[25],
             y = all_centroids_df$c_y[25],

@@

XXX Model in \gD{}, on the UMAP layout, and three views of the fit in projections from $7\text{-}D$, for the S-curve data. The model closely fits the shape, but it has breaks which means that it does not adequately capture the surface. (The **langevitour** software is used to view the data with a tour, and the full video is available at <https://youtu.be/N6iWEj3aVps>). 
:::

@@

The model here is similar to a confirmatory factor analysis model [@brown2015], $\widehat{T}(X_1, X_2, X_3) + \Epsilon$. The difference between the fitted model and observed values would be considered to be residuals, and for this problem are $7\text{-}D$.

### 2024-07-18 paper.tex
Added CFA citations
Update Figure4 with quollr 0.1.5

\caption{\label{fig-scurve-sc}XXX Model in \gD{}, on the UMAP layout,
and three views of the fit in projections from \(7\text{-}D\), for the
S-curve data. The model closely fits the shape, but it has breaks which
means that it does not adequately capture the surface. (The
\textbf{langevitour} software is used to view the data with a tour, and
the full video is available at (\url{https://youtu.be/N6iWEj3aVps}).}

@@

The model here is similar to a confirmatory factor analysis model (REF),
\(\widehat{T}(X_1, X_2, X_3) + \Epsilon\). The difference between the
fitted model and observed values would be considered to be residuals,
and for this problem are \(7\text{-}D\).

>>>>

\caption{\label{fig-scurve-sc}XXX Model in \gD{}, on the UMAP layout,
and three views of the fit in projections from \(7\text{-}D\), for the
S-curve data. The model closely fits the shape, but it has breaks which
means that it does not adequately capture the surface. (The
\textbf{langevitour} software is used to view the data with a tour, and
the full video is available at \url{https://youtu.be/N6iWEj3aVps}).}

@@

The model here is similar to a confirmatory factor analysis model
\citep{brown2015}, \(\widehat{T}(X_1, X_2, X_3) + \Epsilon\). The
difference between the fitted model and observed values would be
considered to be residuals, and for this problem are \(7\text{-}D\).
